Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-25 paper/main.tex
add Epstein (2019) review to references

%#12 RSC + LOC
Apart from the PPA, results show significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
lateral occipital cortex (LOC; more lateral in the movie stimulus, more medial
in the audio-description stimulus) for both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic
activity in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews)
% not random shit
Thus, our model-driven approach to operationalize spatial perception based on
stimulus annotations reveals focussed activation patterns in networks that are
implicated in visual spatial perception and cognition.

@@

\todo[inline]{mir das Potential (warum ist das relevant -> rich stimulus ie many
possible analyses, better compliance, easier to perform for difficult
populations, etc) eigentlich zu kurz}

>>>>

%#12 RSC + LOC
Apart from the PPA, results show significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
lateral occipital cortex (LOC; more lateral in the movie stimulus, more medial
in the audio-description stimulus) for both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic
activity in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role, epstein2019scene} for
reviews)
% not random shit
Thus, our model-driven approach to operationalize spatial perception based on
stimulus annotations reveals focussed activation patterns in networks that are
implicated in visual spatial perception and cognition.

@@

\todo[inline]{SE: mir das Potential (warum ist das relevant -> rich stimulus ie
many possible analyses, better compliance, easier to perform for difficult
populations, etc) eigentlich zu kurz; COH: finde ich (insb. als allerletzten)
Satz in einem Satz so okay, weil a) Textlimit, b) exploratory \& <80 \%
lokalisationsleistung; wenn, dann müsste man ein größeres Fass in Intro und
Discussion aufmachen, was die Ergebnisse aber nicht hergeben }
